---
title: "rotterdam"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## data

```{r}
library(survival)
#library(devtools)
#install_github("FJRubio67/HazReg")
library(HazReg)
# attach the data called 'rotterdam'
attach(rotterdam)
```

```{r}
# Get the new data frame
df <- data.frame(time = rotterdam$dtime, status = rotterdam$death)
# Transform the status into a logical setting
# whether it was observed or not into true or false
df$status <- as.logical(rotterdam$death)
# Get the time in years
df$time <- df$time/365.25

# Required quantities
status <- as.logical(df$status)
survtimes <- df$time
```

## Descriptive Statistical Analysis

```{r}
# survival time analysis
summary(survtimes)

# Age analysis
# Set up a nice-looking plot
par(mfrow=c(1,1),
    mar=c(5,5,2,2),
    cex.lab=1.2,
    cex.axis=1.1,
    cex.main=1.5)
# Draw the histogram
hist(rotterdam$age,
     xlab="Age",
     ylab="Frequency",
     main="Age Distribution",
     col="lightblue",
     border="black",
     breaks=30,
     xlim=c(min(rotterdam$age), max(rotterdam$age)),
     prob=FALSE)
# Add a grid line
grid(nx=NA, ny=NULL, col="gray", lty="dotted",lwd=par("lwd"))
# Add a box around the plot
box()

# Calculate the correlation coefficient between age and nodes
corr<-cor(rotterdam$age,rotterdam$nodes)
print(corr)

```



## KM method

```{r}
# Kaplan-Meier estimator for the survival times
km <- survfit(Surv(survtimes, status) ~ 1)
# See a basic result
km
# Plot the Kaplan-Maier survival curve
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival probability", 
     main = "Kaplan-Maier survival curve")

```

```{r}
# Find the median survival time
median_time <- summary(km)$table["median"]
CI1<-summary(km)$table["0.95LCL"]
CI2<-summary(km)$table["0.95UCL"]
# Plot the Kaplan-Maier survival curve
plot(km,lwd = 2, lty = 1, ylim = c(0,1), 
     xlab = "Time in years", ylab = "Survival probability", 
     main = "Kaplan-Maier survival curve")
abline(h=0.5, col="red",lty=2)
segments(x0=median_time,x1=median_time,y0=0,y1=0.5,col="purple",lty=2)
segments(x0=CI1,x1=CI1,y0=0,y1=0.5,col="blue",lty=2)
segments(x0=CI2,x1=CI2,y0=0,y1=0.5,col="blue",lty=2)
# Add the x values directly to the plot
text(x=median_time,y=0.3,labels = paste("Median:",round(median_time,1)),col = "purple")
text(x=CI1,y=0.7,labels = paste("95% CI Lower:",round(CI1,1)),col = "blue")
text(x=CI2,y=0.6,labels = paste("95% CI Upper:",round(CI2,1)),col = "blue")
# Add the legend
legend("topright",legend = c("Survival Curve","95% confidence interval line"),
                             lty = c(1,2))

```

```{r}
library(survminer)
df$meno <- as.logical(rotterdam$meno)
meno <- as.logical(df$meno)
km1<-survfit(Surv(survtimes, status) ~ meno)
# Plot the Kaplan-Maier survival curve
ggsurvplot(km1,data = rotterdam, xlab = "Time in years",
           ylab = "Survival Probability",lwd = 2,lty = 1,
           surv.median.line='hv',conf.int=TRUE, add.all = TRUE)
```




## Weibull distribution

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Weibull distribution
#--------------------------------------------------------------------------------------------------

# Initial value
initW <- c(0,0)

# Optimisation step using method called 'nlminb'
OPTW <- WMLE(initW, survtimes, status, hstr = "W", method = "nlminb", maxit = 10000)

# MLE
# Using the Exponential function
# Convert two parameters to be positive
MLEW <- c(exp(OPTW$OPT$par[1]), exp(OPTW$OPT$par[2]))

# Fitted Weibull hazard function
fithW <- Vectorize(function(t) hweibull( t, MLEW[1], MLEW[2] ) )

# Fitted Weibull survival function
# S(t)=exp^(-H(t)) 
fitsW <- Vectorize(function(t) exp(-chweibull( t, MLEW[1], MLEW[2] ) ))

# Calculate the AIC for Weibull distribution
# AIC = ???2*log(L) + 2k
AICW <- 2*OPTW$OPT$objective + 2*length(OPTW$OPT$par)

# Calculate the BIC for Weibull distribution
# BIC = ???2*log(L) + k*log(n) 
BICW <- 2*OPTW$OPT$objective + length(OPTW$OPT$par)*log(length(survtimes))
```

## Log-Normal distribution

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Log-Normal distribution
#--------------------------------------------------------------------------------------------------

# Initial value
initLN <- c(0,0)

# Optimisation step using method called 'nlminb'
OPTLN <- LNMLE(initLN, survtimes, status, hstr = "LN", method = "nlminb", maxit = 10000)

# MLE
# Using the Exponential function
# Convert second parameter to be positive
MLELN <- c(OPTLN$OPT$par[1], exp(OPTLN$OPT$par[2]))

# Fitted Log-Normal hazard function
fithLN <- Vectorize(function(t) hlnorm( t, MLELN[1], MLELN[2] ) )

# Fitted Log-Normal survival function
# S(t)=exp^(-H(t)) 
fitsLN <- Vectorize(function(t) exp(-chlnorm( t, MLELN[1], MLELN[2] ) ))

# Calculate the AIC for Log-Normal distribution
# AIC = ???2*log(L) + 2k
AICLN <- 2*OPTLN$OPT$objective + 2*length(OPTLN$OPT$par)

# Calculate the BIC for Log-Normal distribution
# BIC = ???2*log(L) + k*log(n) 
BICLN <- 2*OPTLN$OPT$objective + length(OPTLN$OPT$par)*log(length(survtimes))
```

## Log-Logistic distribution

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Log-Logistic distribution
#--------------------------------------------------------------------------------------------------

# Initial value
initLL <- c(0,0)

# Optimisation step using method called 'nlminb'
OPTLL <- LLMLE(initLL, survtimes, status, hstr = "LL", method = "nlminb", maxit = 10000)

# MLE
# Using the Exponential function
# Convert second parameter to be positive
MLELL <- c(OPTLL$OPT$par[1], exp(OPTLL$OPT$par[2]))

# Fitted Log-Logistic hazard function
fithLL <- Vectorize(function(t) hllogis( t, MLELL[1], MLELL[2] ) )

# Fitted Log-Logistic survival function
# S(t)=exp^(-H(t)) 
fitsLL <- Vectorize(function(t) exp(-chllogis( t, MLELL[1], MLELL[2] ) ))

# Calculate the AIC for Log-Logistic distribution
# AIC = ???2*log(L) + 2k
AICLL <- 2*OPTLL$OPT$objective + 2*length(OPTLL$OPT$par)

# Calculate the BIC for Log-Logistic distribution
# BIC = ???2*log(L) + k*log(n) 
BICLL <- 2*OPTLL$OPT$objective + length(OPTLL$OPT$par)*log(length(survtimes))
```

## Kumaraswamy distribution

```{r}
#########################################################################################
# Kumaraswamy distribution
# Parameters
#########################################################################################
# a > 0
# b > 0
# 0 < x < 1
#########################################################################################

#------------------------------------------------------------------
# PDF
# f(x;a,b) = a*b*x^(a-1)*(1-x^a)^(b-1)
#------------------------------------------------------------------

dkuma <- Vectorize(function(x,a,b,log = FALSE){
  logden <-  log(a) + log(b) + (a-1)*log(x) + (b-1)*log(1-x^a)
  val <- ifelse(log, logden, exp(logden)) 
  return(val)
})

#------------------------------------------------------------------
# CDF
# F(q;a,b) = 1-(1-q^a)^b
#------------------------------------------------------------------

pkuma <- Vectorize(function(q,a,b,log.p = FALSE){
  cdf <-  1 - (1-q^a)^b
  val <- ifelse(log.p, log(cdf), cdf)
  return(val)
})
```

## Generalised Weibull hazard and cumulative hazard(with Kumaraswamy distribution)

```{r}
###############################################################
# Generalised Weibull hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the Kumaraswamy distribution
# b : shape parameter of the Kumaraswamy distribution
# log: log scale (TRUE or FALSE)

# Generalised Weibull hazard function
# h_hat(t)=(p(S(t))f(t))/P(S(t))*h(t)
# p and P are the pdf and cdf of the Kumaraswamy distribution respectively
# S(t) is the survival function of the Weibull distribution 
# f(t) and h(t) are pdf and hazard function of the Weibull distribution
khgwei <- function (t, mu, sigma, a, b, log = FALSE) 
{
 # Take the logarithm of the h(t)
 whaz <- hweibull(t, mu, sigma, log = TRUE)
 # Get the form that is (-H(t))
 wSt <- -chweibull(t, mu, sigma)
 # Get the Weibull survival function
 Stw <- exp( wSt ) 
 # Take the logarithm of the (p(S(t))f(t))/P(S(t))
 wweight <- dkuma(Stw,a,b,log=TRUE) + wSt - 
            pkuma(Stw,a,b,log.p=TRUE)
 # Take the logarithm of the h_hat(t)
 val <- wweight + whaz
  # if log is false, it is going to return to exponential of value
  if (log) 
    return(val)
  else return(exp(val))
}

# S(t)=exp^(-H(t)) 
# S(t): the survival function of the Weibull distribution
# H(t): the cumulative hazard function of the Weibull distribution
# Generalised Weibull survival function
# S_hat(t)=P(S(t))
# P: the cdf of the Kumaraswamy distribution
kchgwei <- function (t, mu, sigma, a, b) 
{
  # Get the form that is S(t)
  Stw <- exp(-chweibull(t, mu, sigma) )
  # H_hat(t)=-log(S_hat(t))=-log(P(S(t)))
  val <- -pkuma(Stw,a,b,log.p=TRUE)
    return(val)
}

```

## Generalised Weibull distribution with Kumaraswamy

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Weibull distribution
# Using the Kumaraswamy distribution as P
#--------------------------------------------------------------------------------------------------

# Obtain the observed survival times that are not censored
tobs <- survtimes[status]

# Get the negative of the log likelihood function
wei_GWK <- function(par){
    # Parameterize the positive parameters
    # Get the new mu, new sigma, new alpha and new beta
    m0 <- exp(par[1])
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    # Adding parameters to the original model
    lhaz0 <- khgwei(tobs, m0,s0,a0,b0, log = TRUE)
    # Log the expression for the likelihood function
    # -log likelihood=-sum(log(h_hat(t)))+sum(H_hat(t))
    val <- -sum(lhaz0) + sum(kchgwei(survtimes,m0,s0,a0,b0))
    return(val)
  
}

# Initial value
# The value are close to the maximum likelihood estimator
initGWK <- c(OPTW$OPT$par,0,0)

# Optimisation step
# Although the 'nlminb' finds the minimum of a function
# Finding the maximum of a function is the same as finding the minimum of the negative of that function
OPTGWK <- nlminb(initGWK, wei_GWK, control = list(iter.max = 10000))

# MLE
# The parameters need to be exponentiated
MLEGWK <- c(exp(OPTGWK$par[1:4]))

# Fitted Generalised Weibull hazard function
fithGWK <- Vectorize(function(t) khgwei( t, MLEGWK[1], MLEGWK[2], MLEGWK[3], MLEGWK[4] ) )

# Fitted Generalised Weibull survival function
fitsGWK <- Vectorize(function(t) exp(-kchgwei( t, MLEGWK[1], MLEGWK[2], MLEGWK[3], MLEGWK[4] ) ))

# Calculate the AIC for the generalised Weibull distribution with Kumaraswamy distribution
# AIC = ???2*log(L) + 2k
AICGWK <- 2*OPTGWK$objective + 2*length(OPTGWK$par)

# Calculate the BIC for the generalised Weibull distribution with Kumaraswamy distribution
# BIC = ???2*log(L) + k*log(n) 
BICGWK <- 2*OPTGWK$objective + length(OPTGWK$par)*log(length(survtimes))

```

## comparison

```{r}
#############################################################################
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICW,AICGWK)
c(BICW,BICGWK)

# Plot the KM-method survival curve
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
# Fitted survival functions with Weibull distribution as red line
curve(fitsW, 0, 20, add = TRUE, lwd = 2, col = "red")
# # Fitted survival functions with generalised Weibull distribution as blue line
curve(fitsGWK, 0, 20, add = TRUE, lwd = 2, col = "blue")
# Make a legend to explain
legend("topright", legend = c("KM","W","GWK"), col = c("black", "red", "blue"), lwd = c(2,2,2))

# Fitted hazard functions with Weibull distribution as red line
curve(fithW, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
# Fitted hazard functions with generalised Weibull distribution as blue line
curve(fithGWK, 0, 20, add = TRUE, lwd = 2, col = "blue")
# Make a legend to explain
legend("bottomright", legend = c("W","GWK"), col = c("red","blue"), lwd = c(2,2))

```

## Generalised Log-Normal hazard and cumulative hazard(with Kumaraswamy distribution)

```{r}
###############################################################
# Generalised Log-Normal hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the Kumaraswamy distribution
# b : shape parameter of the Kumaraswamy distribution
# log: log scale (TRUE or FALSE)

# Use the same method that define khgwei and kchgwei to define khglnormal and kchglnormal
khglnormal <- function (t, mu, sigma, a, b, log = FALSE) 
{
 lnhaz <- hlnorm(t, mu, sigma, log = TRUE)
 lnSt <- -chlnorm(t, mu, sigma)
 nSt <- exp( lnSt ) 
 lnweight <- dkuma(nSt,a,b,log=TRUE) + lnSt - 
             pkuma(nSt,a,b,log.p=TRUE)
 
 val <- lnweight + lnhaz
  
  if (log) 
    return(val)
  else return(exp(val))
}

kchglnormal<- function (t, mu, sigma, a, b) 
{
  Stn <- exp(-chlnorm(t, mu, sigma) )
  val <- -pkuma(Stn,a,b,log.p=TRUE)
    return(val)
}
```

## Generalised Log-Normal distribution

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Log-Normal distribution
# Using the Kumaraswamy distribution as P
#--------------------------------------------------------------------------------------------------

# Negative Log likelihood
log_likGLNK <- function(par){
  
    m0 <- par[1]
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    
    lnhaz0 <- khglnormal(tobs, m0,s0,a0,b0, log = TRUE)
    val <- -sum(lnhaz0) + sum(kchglnormal(survtimes,m0,s0,a0,b0))
    return(val)
  
}

# Initial value
initGLNK <- c(OPTLN$OPT$par,0,0)

# Optimisation step
OPTGLNK <- nlminb(initGLNK, log_likGLNK, control = list(iter.max = 10000))

# MLE
# The first one is already in the parameterization
# The others need to be exponentiated
MLEGLNK <- c(OPTGLNK$par[1], exp(OPTGLNK$par[2:4]))

# Fitted Generalised Log-Normal hazard function
fithGLNK <- Vectorize(function(t) khglnormal( t, MLEGLNK[1], MLEGLNK[2], MLEGLNK[3], MLEGLNK[4] ) )

# Fitted Generalised Log-Normal survival function
fitsGLNK <- Vectorize(function(t) exp(-kchglnormal( t, MLEGLNK[1], MLEGLNK[2], MLEGLNK[3], MLEGLNK[4] ) ))

# AIC for the generalised Log-Normal distribution with Kumaraswamy distribution
AICGLNK <- 2*OPTGLNK$objective + 2*length(OPTGLNK$par)

# BIC for the generalised Log-Normal distribution with Kumaraswamy distribution
BICGLNK <- 2*OPTGLNK$objective + length(OPTGLNK$par)*log(length(survtimes))

```

## conparison (LN GLN)

```{r}
#############################################################################
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICLN,AICGLNK)
c(BICLN,BICGLNK)

# Fitted survival functions with Log-Normal distribution and generalised Log-Normal distribution
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
curve(fitsLN, 0, 20, add = TRUE, lwd = 2, col = "red")
curve(fitsGLNK, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("KM","LN","GLNK"), col = c("black","red","blue"), lwd = c(2,2,2))

# Fitted hazard functions with Log-Normal distribution and generalised Log-Normal distribution
curve(fithLN, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
curve(fithGLNK, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("LN","GLNK"), col = c("red","blue"), lwd = c(2,2))
```

## Generalised Log-Logistic hazard and cumulative hazard

```{r}
###############################################################
# Generalised Log-Logistic hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the Kumaraswamy distribution
# b : shape parameter of the Kumaraswamy distribution
# log: log scale (TRUE or FALSE)

# Use the same method that define khgwei and kchgwei to define khgllogis and kchgllogis
khgllogis <- function (t, mu, sigma, a, b, log = FALSE) 
{
 lhaz <- hllogis(t, mu, sigma, log = TRUE)
 lSt <- -chllogis(t, mu, sigma)
 St <- exp( lSt ) 
 lweight <- dkuma(St,a,b,log=TRUE) + lSt - 
            pkuma(St,a,b,log.p=TRUE)
 
 val <- lweight + lhaz
  
  if (log) 
    return(val)
  else return(exp(val))
}

kchgllogis <- function (t, mu, sigma, a, b) 
{
  St <- exp(-chllogis(t, mu, sigma) )
  val <- -pkuma(St,a,b,log.p=TRUE)
    return(val)
}

```

## Genaraised Log-Logistic and Kumaraswamy distribution

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Log-Logistic distribution
# Using the Kumaraswamy distribution as P
#--------------------------------------------------------------------------------------------------

# Negative Log likelihood
log_likGLLK <- function(par){

    m0 <- par[1]
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    
    lhaz0 <- khgllogis(tobs, m0,s0,a0,b0, log = TRUE)
    
    val <- -sum(lhaz0) + sum(kchgllogis(survtimes,m0,s0,a0,b0))
    return(val)
  
}

# Initial value
initGLLK <- c(OPTLL$OPT$par,1,1)

# Optimisation step
OPTGLLK <- nlminb(initGLLK, log_likGLLK, control = list(iter.max = 10000))

# MLE
# The first one is already in the parameterization
# The others need to be exponentiated
MLEGLLK <- c(OPTGLLK$par[1], exp(OPTGLLK$par[2:4]))

# Fitted Generalised Log-Logistic hazard function
fithGLLK <- Vectorize(function(t) khgllogis( t, MLEGLLK[1], MLEGLLK[2], MLEGLLK[3], MLEGLLK[4] ) )

# Fitted Generalised Log-Logistic survival function
fitsGLLK <- Vectorize(function(t) exp(-kchgllogis( t, MLEGLLK[1], MLEGLLK[2], MLEGLLK[3], MLEGLLK[4] ) ))

# AIC for the generalised Log-Logistic distribution with Kumaraswamy distribution
AICGLLK <- 2*OPTGLLK$objective + 2*length(OPTGLLK$par)

# BIC for the generalised Log-Logistic distribution with Kumaraswamy distribution
BICGLLK <- 2*OPTGLLK$objective + length(OPTGLLK$par)*log(length(survtimes))

```

## comparison

```{r}
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICLL,AICGLLK)
c(BICLL,BICGLLK)

# Fitted survival functions with Log-Logistic distribution and generalised Log-Logisticl distribution
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
curve(fitsLL, 0, 20, add = TRUE, lwd = 2, col = "red")
curve(fitsGLLK, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("KM","LL","GLLK"), col = c("black","red","blue"), lwd = c(2,2,2))

# Fitted hazard functions with Log-Logistic distribution and generalised Log-Logisticl distribution
curve(fithLL, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
curve(fithGLLK, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("LL","GLLK"), col = c("red","blue"), lwd = c(2,2))

```

## Genaralised Weibull hazard and cumulative hazard(with beta distribution)

```{r}
###############################################################
# Generalised Weibull hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the beta distribution
# b : shape parameter of the beta distribution
# log: log scale (TRUE or FALSE)

# Use the same method that define khgwei and kchgwei to define bhgwei and bchgwei
bhgwei <- function (t, mu, sigma, a, b, log = FALSE) 
{
 whaz <- hweibull(t, mu, sigma, log = TRUE)
 wSt <- -chweibull(t, mu, sigma)
 Stw <- exp( wSt ) 
 wweight <- dbeta(Stw,a,b,log=TRUE) + wSt - 
            pbeta(Stw,a,b,log.p=TRUE)
 
 val <- wweight + whaz
  
  if (log) 
    return(val)
  else return(exp(val))
}

bchgwei <- function (t, mu, sigma, a, b) 
{
  Stw <- exp(-chweibull(t, mu, sigma) )
  val <- -pbeta(Stw,a,b,log.p=TRUE)
    return(val)
}

```

## Generalised Weibull distribution and beta distribution as P

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Weibull distribution
# Using the Beta distribution as P
#--------------------------------------------------------------------------------------------------

# Negative Log likelihood
wei_GWB <- function(par){

    m0 <- exp(par[1])
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    
    lhaz0 <- bhgwei(tobs, m0,s0,a0,b0, log = TRUE)
    
    
    val <- -sum(lhaz0) + sum(bchgwei(survtimes,m0,s0,a0,b0))
    return(val)
  
}


# Initial value
initGWB <- c(OPTW$OPT$par,0,0)

# Optimisation step
OPTGWB <- nlminb(initGWB, wei_GWB, control = list(iter.max = 10000))

# MLE
MLEGWB <- c(exp(OPTGWB$par[1:4]))

# Fitted Generalised Weibull hazard function
fithGWB <- Vectorize(function(t) bhgwei( t, MLEGWB[1], MLEGWB[2], MLEGWB[3], MLEGWB[4] ) )

# Fitted Generalised Weibull survival function
fitsGWB <- Vectorize(function(t) exp(-bchgwei( t, MLEGWB[1], MLEGWB[2], MLEGWB[3], MLEGWB[4] ) ))

# AIC for the generalised Weibull distribution with beta distribution
AICGWB <- 2*OPTGWB$objective + 2*length(OPTGWB$par)

# BIC for the generalised Weibull distribution with beta distribution
BICGWB <- 2*OPTGWB$objective + length(OPTGWB$par)*log(length(survtimes))

```

## comparison

```{r}
#############################################################################
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICW,AICGWB)
c(BICW,BICGWB)

# Fitted survival functions
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
curve(fitsW, 0, 20, add = TRUE, lwd = 2, col = "red")
curve(fitsGWB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("KM","W","GWB"), col = c("black","red","blue"), lwd = c(2,2,2))

# Fitted hazard functions
curve(fithW, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
curve(fithGWB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("bottomright", legend = c("W","GWB"), col = c("red","blue"), lwd = c(2,2))

```

## Generalised Log-Normal hazard and cumulative hazard(with beta distribution)

```{r}
###############################################################
# Generalised Log-Normal hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the beta distribution
# b : shape parameter of the beta distribution
# log: log scale (TRUE or FALSE)

# Use the same method that define khgwei and kchgwei to define bhglnormal and bchglnormal
bhglnormal <- function (t, mu, sigma, a, b, log = FALSE) 
{
 lnhaz <- hlnorm(t, mu, sigma, log = TRUE)
 lnSt <- -chlnorm(t, mu, sigma)
 nSt <- exp( lnSt ) 
 lnweight <- dbeta(nSt,a,b,log=TRUE) + lnSt - 
             pbeta(nSt,a,b,log.p=TRUE)
 
 val <- lnweight + lnhaz
  
  if (log) 
    return(val)
  else return(exp(val))
}

bchglnormal<- function (t, mu, sigma, a, b) 
{
  Stn <- exp(-chlnorm(t, mu, sigma) )
  val <- -pbeta(Stn,a,b,log.p=TRUE)
    return(val)
}
```

## Generalised Log-Normal distribution and Beta distribution as P

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Log-Normal distribution
# Using the beta distribution as P
#--------------------------------------------------------------------------------------------------

# Negative Log likelihood

log_likGLNB <- function(par){

    m0 <- par[1]
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    
    lnhaz0 <- bhglnormal(tobs, m0,s0,a0,b0, log = TRUE)
    
    
    val <- -sum(lnhaz0) + sum(bchglnormal(survtimes,m0,s0,a0,b0))
    return(val)
  
}


# Initial value
initGLNB <- c(OPTLN$OPT$par,0,0)

# Optimisation step
OPTGLNB <- nlminb(initGLNB, log_likGLNB, control = list(iter.max = 10000))

# MLE
MLEGLNB <- c(OPTGLNB$par[1], exp(OPTGLNB$par[2:4]))

# Fitted Generalised Log-Normal hazard function
fithGLNB <- Vectorize(function(t) bhglnormal( t, MLEGLNB[1], MLEGLNB[2], MLEGLNB[3], MLEGLNB[4] ) )

# Fitted Generalised Log-Normal survival function
fitsGLNB <- Vectorize(function(t) exp(-bchglnormal( t, MLEGLNB[1], MLEGLNB[2], MLEGLNB[3], MLEGLNB[4] ) ))

# AIC for the generalised Log-Normal distribution with beta distribution
AICGLNB <- 2*OPTGLNB$objective + 2*length(OPTGLNB$par)

# BIC for the generalised Log-Normal distribution with beta distribution
BICGLNB <- 2*OPTGLNB$objective + length(OPTGLNB$par)*log(length(survtimes))

```

## conparison

```{r}
#############################################################################
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICLN,AICGLNB)
c(BICLN,BICGLNB)

# Fitted survival functions
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
curve(fitsLN, 0, 20, add = TRUE, lwd = 2, col = "red")
curve(fitsGLNB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("KM","LN","GLNB"), col = c("black","red","blue"), lwd = c(2,2,2))

# Fitted hazard functions
curve(fithLN, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
curve(fithGLNB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("LN","GLNB"), col = c("red","blue"), lwd = c(2,2))
```

## Generalised Log-Logistic hazard and cumulative hazard(with beta distribution)

```{r}
###############################################################
# Generalised Log-Logistic hazard and cumulative hazard
###############################################################

# t : positive argument
# mu : mean parameter in the log scale
# sigma : scale parameter in the log scale
# a : shape parameter of the beta distribution
# b : shape parameter of the beta distribution
# log: log scale (TRUE or FALSE)

# Use the same method that define khgwei and kchgwei to define bhgllogis and bchgllogis
bhgllogis <- function (t, mu, sigma, a, b, log = FALSE) 
{
 lhaz <- hllogis(t, mu, sigma, log = TRUE)
 lSt <- -chllogis(t, mu, sigma)
 St <- exp( lSt ) 
 lweight <- dbeta(St,a,b,log=TRUE) + lSt - 
            pbeta(St,a,b,log.p=TRUE)
 
 val <- lweight + lhaz
  
  if (log) 
    return(val)
  else return(exp(val))
}

bchgllogis <- function (t, mu, sigma, a, b) 
{
  St <- exp(-chllogis(t, mu, sigma) )
  val <- -pbeta(St,a,b,log.p=TRUE)
    return(val)
}
```

## Generalised Log-Logistic distribution and Beta distribution as P

```{r}
#--------------------------------------------------------------------------------------------------
# Fitting a Generalised Log-Logistic distribution
# Using the beta distribution as P
#--------------------------------------------------------------------------------------------------

# Negative Log likelihood

log_likGLLB <- function(par){

    m0 <- par[1]
    s0 <- exp(par[2])
    a0 <- exp(par[3])
    b0 <- exp(par[4])
    
    lhaz0 <- bhgllogis(tobs, m0,s0,a0,b0, log = TRUE)
    
    
    val <- -sum(lhaz0) + sum(bchgllogis(survtimes,m0,s0,a0,b0))
    return(val)
  
}


# Initial value
initGLLB <- c(OPTLL$OPT$par,1,1)

# Optimisation step
OPTGLLB <- nlminb(initGLLB, log_likGLLB, control = list(iter.max = 10000))

# MLE
MLEGLLB <- c(OPTGLLB$par[1], exp(OPTGLLB$par[2:4]))

# Fitted Generalised Log-Logistic hazard function
fithGLLB <- Vectorize(function(t) bhgllogis( t, MLEGLLB[1], MLEGLLB[2], MLEGLLB[3], MLEGLLB[4] ) )

# Fitted Generalised Log-Logistic survival function
fitsGLLB <- Vectorize(function(t) exp(-bchgllogis( t, MLEGLLB[1], MLEGLLB[2], MLEGLLB[3], MLEGLLB[4] ) ))

# AIC for the generalised Log-Normal distribution with beta distribution
AICGLLB <- 2*OPTGLLB$objective + 2*length(OPTGLLB$par)

# BIC for the generalised Log-Normal distribution with beta distribution
BICGLLB <- 2*OPTGLLB$objective + length(OPTGLLB$par)*log(length(survtimes))

```

## comparison

```{r}
# comparison
#############################################################################

# Model selection using AIC and BIC
c(AICLL,AICGLLB)
c(BICLL,BICGLLB)

# Fitted survival functions
plot(km$time, km$surv, type = "l", col = "black", lwd = 2, lty = 1, 
     ylim = c(0,1), xlab = "Time in years", ylab = "Survival")
curve(fitsLL, 0, 20, add = TRUE, lwd = 2, col = "red")
curve(fitsGLLB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("KM","LL","GLLB"), col = c("black","red","blue"), lwd = c(2,2,2))

# Fitted hazard functions
curve(fithLL, 0, 20, lwd = 2, col = "red", ylim = c(0,0.1), ylab = "Hazard", xlab = "Time in years")
curve(fithGLLB, 0, 20, add = TRUE, lwd = 2, col = "blue")
legend("topright", legend = c("LL","GLLB"), col = c("red","blue"), lwd = c(2,2))

```


